### 2022-11-19 dissertation/chapters/08-results.tex
🚧 (results): Bigger font sizes

The required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}. The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experimental groups to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics. The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

Finally, this chapter provides the outcome of these empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for the discussions. The output of the statistical analysis that yielded the results that is presented in the chapter is provided in Appendix~\ref{app:statistical_analysis}. The remainder of the chapter is structured as follows.

\begin{itemize}
	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}. Illustrations are provided to show the change in parameter values to illustrate the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.

	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics as it relates to all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.

@@

	\item \textbf{Section \ref{sec:results:practical_applications}} provides a brief discussion on the practical application of the \acs{BHH} to real-world problems.

@@

@@

This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset. As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records. The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process. Some noisiness can be expected as mini-batch training is executed with batch sizes of 30. The results that are presented are averaged over 30 independent runs.

Furthermore, the case study focuses on three different variants of the \acs{BHH}. These include the baseline configuration as was provided in Chapter~\ref{chap:bhh}, as well as a configuration that includes a ``long memory'' by setting the replay window size to 250, and a configuration that makes use of the \textit{symmetric} credit assignment strategy. These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment is chosen to illustrate a case where there \acs{BHH} does not reward good performance and does not yield a bias towards \index{heuristic}heuristics that perform well. This section is structured as follows.

@@

	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning process implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METRICS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance metrics}\label{sec:results:case_study:performance_metrics}

Figures~\ref{fig:results:case_study:train_loss}-\ref{fig:results:case_study:test_accuracy} provide illustrations of the train and test, loss and accuracy plots over 30 epochs and is illustrated in log scale. The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}. The noisiness that results from mini-batch training can be observed in Figure~\ref{fig:results:case_study:test_loss}. Figures~\ref{fig:results:case_study:train_accuracy} and~\ref{fig:results:case_study:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%. Although the \acs{BHH} was able to succesfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration. However, it should be noted from epochs 5 and onwards presented in Figure~\ref{fig:results:case_study:test_accuracy} that all the configurations of the \acs{BHH} was able to ``undo'' selections that yielded worse test loss results in the previous epoch. The sporadic, oscillating nature of the results later in the training process is simply a result of momentum that is maintained between low-level \index{heuristic}heuristics. For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions. The \acs{BHH} does not incorporate a \textit{move acceptance} strategy, whereby a heuristic's outcome is rejected if it does not improve on previous results, yielding a possibly worse loss measurement. A move acceptance strategy can be utilised on a validation set as a mechanism to approve or reject heuristic progressions from one step to the other.

Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figures~\ref{fig:results:case_study:train_loss}-\ref{fig:results:case_study:test_accuracy} only provide the outcomes of performance metrics at the end of each epoch. Further investigation is required at a mini-batch step level.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
	\caption{The average training loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:train_loss}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
	\caption{The average test loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:test_loss}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
	\caption{The average training accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:train_accuracy}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
	\caption{The average test accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:test_accuracy}
\end{figure}

@@

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, from which prior \textit{probabilities of selection probabilities} are sampled. Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, 8 respectively. Index 0, 6, 7, 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the concentration parameters in $\boldsymbol{\alpha}$ and the \index{heuristic pool}heuristic pool. Simular illustrations for the other indices in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:8}
\end{figure}

The first logical observation to be made from Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} is the step-wise increasing nature of $\boldsymbol{\alpha}$ for the long memory configuration (denoted \textit{bhh\_replay\_250}), illustrated in green. Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics. The values in $\boldsymbol{\alpha}$ is never reset to its initial value of 1, and thus $\boldsymbol{\alpha}$ continues to increase throughout the training process. However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$. The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}. Heuristics that perform will will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.

The next observation that can be made is for the baseline configuration (denoted \textit{bhh\_baseline}) in red, and the symmetric credit assignment strategy configuration (denoted \textit{bhh\_credit\_symmetric}) in blue. Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1 as regular intervals. This interval is represented by the \textit{reanalysis} window size. The reanalysis interval dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}. Bayesian analysis is used to update $\boldsymbol{\alpha}$. As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change. Notice that $\boldsymbol{\alpha} \geq 1$ for multiple indices, even after reanalysis. This is because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1 at the corresponding index in $\boldsymbol{\alpha}$ through the Bayesian analysis process. In a case where all 5 entities in the entity pool are allocated the same heuristic, for all 10 steps in the reanalysis windown, $\boldsymbol{\alpha} = 50$.

Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning. The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurance} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$). \index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the probabilistic sampling nature of the \acs{BHH}. Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.

@@

This section provides a detailed investigation into the \textit{probabilities of selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves. The probability distribution of \index{heuristic}heuristic selection probabilities is denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8} provide illustrations of the probabilities of the selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, 8 represent the probabilities of selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and the \index{heuristic pool}heuristic pool. Once again, simular illustrations for the other indices in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

From the illustrations presented in Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8}, a clearer picture off the learning process of the \acs{BHH} is formed. The first important observation to make is for the bhh\_replay\_250 configuration, presented in green. As a reminder, 10 low-level \index{heuristic}heuristics are included in the heuristic pool, yielding a probability of selection probability of 0.1 for each \index{heuristic}heuristic by the frequentist view of probabilistic modeling. Towards the end of the training process, the probability of selection probability converges back to the symmetrical, uniform probability distribution, yielding a probability of selection probability of 0.1 per \index{heuristic}heuristic. This can be explained as follows: most of the training progress is made in the early stages of the training process, and training stagnates towards the end of the training process. Since training stagnates, all heuristics, no matter their past performances, struggle to yield better solutions towards the end of the training process. As a result of stagnation, heuristics then struggle to yield credit allocations by means of the credit assignment strategy. In the case study experimental group, both the bhh\_baseline and bhh\_replay\_250 configurations make use of the \textit{ibest} credit assignment strategy. The \textit{ibest} credit assignment strategy allocates credit to the heuristic that provided the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance. However, since the bhh\_baseline has a short reanalysis interval, the concentration parameter $\boldsymbol{\alpha}$ gets reset to its default value of 1 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is less narrow and thus explaining the larger variance of $\boldsymbol{\theta}$ throughout.

>>>>

The last step in the scientific process requires the presentation of the outcomes of the empirical process. Objective discussions based on statistical analysis of the findings is required. The design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experimental groups to conduct. The experimental groups that were identified include a case study on the behaviour of the \acs{BHH} during training, an empirical comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics, and a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

This chapter provides the outcomes of the empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for discussions. The output of the statistical analysis that yielded the results is provided in Appendix~\ref{app:statistical_analysis}. The remainder of the chapter is structured as follows.

\begin{itemize}
	\item \textbf{Section \ref{sec:results:overview}} provides a brief overview of the outcomes of the empirical process and highlights key aspects to observe in the results.

	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}. Illustrations are provided to show the change in parameter values to illustrate the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.

	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics on all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.

@@

@@

\section{Overview}\label{sec:results:overview}

This section provides a brief discussion on the general outcome of the empirical process as a whole. Overall the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets. In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}. Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.

Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results. The \acs{BHH} applies a form of \index{online learning}online learning. As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process. The training process is not repeated iteratively. All experiments conducted are executed for 30 epochs. The number of training steps executed is dependent on the batch size applied for each dataset.

All of the underlying \acp{FFNN} trained in the empirical process are relatively small. As such, most of the training progress is observed to occur withing the first five epochs. As a result, the \acs{BHH} should apply most learning at the early stages of the training process. After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point. Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the \index{heuristic}heuristic space beyond the five epoch mark.

The \acs{BHH} does not implement a move acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution. In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.

Given the stochastic nature of the \index{heuristic}heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn. This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}. The probabilistic model implements \textit{probabilities of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.

The \textit{reanalysis interval} defines intervals at which the \acs{BHH} reanalyses the performance log, in effect, resetting the concentration parameters to their default values and reapplying the underlying Bayesian analysis process on the performance log. Furthermore, the \textit{replay window size} defines the amount of performance evidence in the performance log. By default, the \acs{BHH} baseline configuration has a reanalysis interval of 10, and a replay window size of 10, which is a small window to learn from. Despite the small reanalysis interval and the small replay window size, it should be observed that the \acs{BHH} exploits small performance biases regardless and does find small performance gains throughout.

@@

This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset. As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records. The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process. Mini-batch training is executed with a batch size of 30. The results that are presented are averaged over 30 independent runs.

Furthermore, the case study focuses on three variants of the \acs{BHH}. These include the baseline configuration, as was provided in Chapter~\ref{chap:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}). Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}). Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).

These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all. This section is structured as follows.

@@

	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning mechanism implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METRICS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}

This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}. Figures~\ref{fig:results:case_study:metrics:train_loss}-\ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test, loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
		\caption{Train log loss}
		\label{fig:results:case_study:metrics:train_loss}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
		\caption{Test log loss}
		\label{fig:results:case_study:metrics:test_loss}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
		\caption{Train log accuracy}
		\label{fig:results:case_study:metrics:train_accuracy}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
		\caption{Test log accuracy}
		\label{fig:results:case_study:metrics:test_accuracy}
	\end{subfigure}
	\par\bigskip
	\caption{The average train and test, loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:metrics}
\end{figure}

The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}, observed by the convergence of the training process, yielding good results. Figures~\ref{fig:results:case_study:metrics:train_accuracy} and~\ref{fig:results:case_study:metrics:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.

Although the different configurations of the \acs{BHH} are all able to succesfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.

The volatility observed in Figure~\ref{fig:results:case_study:metrics:test_loss} is due to overfitting and partly due to the noisiness that results from mini-batch training. Early stopping can be applied to the training process to hault training before the model overfits on the training data. The training dataset is also very small, with just 120 samples. As such, overfitting can be expected.

From Figure~\ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed. This could simply be a result of momentum that is maintained when switching between low-level \index{heuristic}heuristics in an attempt to find better solutions. For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions. The \acs{BHH} does not incorporate a \textit{move acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set. A move acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.

Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure~\ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch. Further investigation is required at a mini-batch step level and is provided in the following sections.

@@

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at index 0, 6, 7, and 8 respectively. Index 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
		\caption{$\alpha_{0}$ - \acs{SGD}}
		\label{fig:results:case_study:alphas:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
		\caption{$\alpha_{6}$ - \acs{Adam}}
		\label{fig:results:case_study:alphas:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
		\caption{$\alpha_{7}$ - \acs{PSO}}
		\label{fig:results:case_study:alphas:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
		\caption{$\alpha_{8}$ - \acs{GA}}
		\label{fig:results:case_study:alphas:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0,6,7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alphas}
\end{figure}

The first logical observation to be made from Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}. Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all. The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process. However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$. The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}. Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.

The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}. Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals. This interval is defined by the \textit{reanalysis interval} hyper-parameter. The reanalysis interval dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}. Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval. As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.

Notice from Figure~\ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements. This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process. Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process. In a case where all five entities in the entity pool are allocated the same heuristic, for all ten samples defined in the performance log, defined by the replay window size, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.

Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning. The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurance} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$). \index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}. Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.

@@

This section provides a detailed investigation into the \textit{probabilities of selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves. The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of the \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool. Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
		\caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
		\label{fig:results:case_study:thetas:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
		\caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
		\label{fig:results:case_study:thetas:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
		\caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
		\label{fig:results:case_study:thetas:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
		\caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
		\label{fig:results:case_study:thetas:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average sampled probabilities of \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8. The probabilities of the \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:thetas}
\end{figure}

From the illustrations presented in Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8}, a clearer picture off the learning process of the \acs{BHH} is formed. The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}. As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected probability of \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modeling.
